Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-05-07 manuscripts/manuscript.Rmd
more replicates

keywords: [optimal control, fisheries, ecological management, adjustment costs]

layout: review,12pt,author-year,titlepage
linenumbers: true
bibliography: components/references.bib
csl: components/ecology.csl
documentclass: components/elsarticle
geometry: [verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,l
margin=2.54cm,rmargin=2.54cm]

@@

library("rmarkdown")
library("pdgControl")
library("reshape2")
library("plyr")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
library("ggthemes")
library("snowfall")
library("tidyr")
library("dplyr")
library("gtable")
library("gridExtra")
library("parallel")
options(digits=2)

@@

```{r parameters, cache=FALSE}
parallel = TRUE
ncpu = parallel::detectCores()
price = 10
c0 = 30
profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
#c2 <- exp(seq(0, log(41), length.out = 40))-1
c2 <- seq(0, 40, length.out=100)
reduction <- 0.25 
seed <- 123                 # Random seed (replicable results)
delta <- 0.05               # economic discounting rate
OptTime <- 50               # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- 0.2              # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
```

```{r analysis, include=FALSE}
source("components/analysis.R")
```

@@

To simplify presentation of the results, we will illustrate cases where the
growth parameters are chosen so that the equilibrium biomass for the equivalent
deterministic model without harvesting is `r (pars[1]-1)/pars[2]`; (specifically, $A=$ `r pars[1]` and
$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}). To characterize environmental variability, we
assume multiplicative shock $Z_t$ is distributed log-normally with
log standard deviation $\sigma_g$ = `r sigma_g`. In addition, we
show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.
In the supplement we illustrate that the qualitative patterns observed
here are not sensitive to the specific choices of these parameter values.

>>>>

layout: review,12pt
linenumbers: true

bibliography: components/references.bib
csl: components/ecology.csl
documentclass: components/elsarticle

@@

library("rmarkdown")
library("pdgControl")
library("reshape2")
library("plyr")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
library("ggthemes")
library("snowfall")
library("tidyr")
library("dplyr")
library("gtable")
library("gridExtra")
options(digits=2)

@@

```{r analysis, include=FALSE}

source("components/analysis.R")
```

@@

To simplify presentation of the results, we will illustrate cases where the
growth parameters are chosen so that the equilibrium biomass for the equivalent
deterministic model without harvesting is `r K`; (specifically, $A=$ `r pars[1]` and
$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}). To characterize environmental variability, we
assume multiplicative shock $Z_t$ is distributed log-normally with
log standard deviation $\sigma_g$ = `r sigma_g`. In addition, we
show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.
In the supplement we illustrate that the qualitative patterns observed
here are not sensitive to the specific choices of these parameter values.
